Analysis and results

### 2020-09-12 analysis/03_analysis.Rmd
I and J index switched in model output (i.e., that's what I get for transposing) but corrected for new posterior draws; removed old figures; plotted new posterior draws

```{r extract-draws, eval=FALSE}
intercept <- 0                            # Intercept-only
public_affairs <- 0                       # Public affairs
political_ideology <- 0                   # Political ideology
social_views <- 0                         # Social views
charity_voluntarism <- 0                  # Charity and voluntarism
demographics <- 0                         # Demographics
public_political <- 0                     # Public affairs + Political ideology
public_political_social <- 0              # + Social views
public_political_social_charity <- 0      # + Charity and voluntarism
public_political_social_charity_demo <- 1 # + Demographics

@@

# Extract posterior draws
draws <- fit %>% 
  spread_draws(Gamma[i, j]) %>% 
  ungroup() %>% 
  filter(.iteration > 500)

@@

```{r load-draws}
intercept <- 1                            # Intercept-only
public_affairs <- 0                       # Public affairs
political_ideology <- 0                   # Political ideology
social_views <- 0                         # Social views
charity_voluntarism <- 0                  # Charity and voluntarism
demographics <- 0                         # Demographics
public_political <- 0                     # Public affairs + Political ideology
public_political_social <- 0              # + Social views
public_political_social_charity <- 0      # + Charity and voluntarism
public_political_social_charity_demo <- 0 # + Demographics

@@

@@

```{r plot-marginals}
# Plot marginals
if (intercept == 1) {
  draws %>%
    mutate(
      levels = factor(j, labels = level_labels)
    ) %>%
    ggplot(aes(x = Gamma, y = levels)) +
    geom_halfeye(.width = .95) +
    geom_vline(xintercept = 0, color = "grey") +
    labs(y = "Attribute Levels")
}
if (intercept != 1) {
  draws %>%
    filter(j != 1) %>%
    mutate(
      levels = factor(i, labels = level_labels),
      covariates = factor(j, labels = covariate_labels)
    ) %>%
    ggplot(aes(x = Gamma, y = covariates)) +
       geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
       # geom_halfeyeh(.width = .95) +
       geom_vline(xintercept = 0, color = "white") +
       labs(y = "Covariates") +
       facet_wrap(~ levels, ncol = 5)
}

# Save plot
if (intercept == 1) file_name <- paste("intercept_marginal-posteriors.png")
if (public_affairs == 1) file_name <- paste("public-affairs_marginal-posteriors.png")
if (political_ideology == 1) file_name <- paste("political-ideology_marginal-posteriors.png")
if (social_views == 1) file_name <- paste("social-views_marginal-posteriors.png")
if (charity_voluntarism == 1) file_name <- paste("charity-voluntarism_marginal-posteriors.png")
if (demographics == 1) file_name <- paste("demographics_marginal-posteriors.png")
if (public_political == 1) file_name <- paste("public-political_marginal-posteriors.png")
if (public_political_social == 1) file_name <- paste("public-political-social_marginal-posteriors.png")
if (public_political_social_charity == 1) file_name <- paste("public-political-social-charity_marginal-posteriors.png")
if (public_political_social_charity_demo == 1) file_name <- paste("public-political-social-charity-demos_marginal-posteriors.png")
ggsave(
  file_name,
  path = here::here("analysis", "output", "figures"),
  width = ifelse(intercept == 1, 12, 20),
  height = ifelse(sum(intercept, public_affairs, political_ideology, social_views, charity_voluntarism, demographics) == 1, 12, 20),
  units = "in"
)
```

>>>>

```{r extract-draws, eval=FALSE}
intercept <- 1                            # Intercept-only
public_affairs <- 0                       # Public affairs
political_ideology <- 0                   # Political ideology
social_views <- 0                         # Social views
charity_voluntarism <- 0                  # Charity and voluntarism
demographics <- 0                         # Demographics
public_political <- 0                     # Public affairs + Political ideology
public_political_social <- 0              # + Social views
public_political_social_charity <- 0      # + Charity and voluntarism
public_political_social_charity_demo <- 0 # + Demographics

@@

# Extract posterior draws
draws <- fit %>% 
  spread_draws(Gamma[i, j]) %>% 
  ungroup() %>% 
  filter(.iteration > 500) %>% 
  rename(
    i = j,
    j = i
  )

@@

```{r load-draws}
intercept <- 0                            # Intercept-only
public_affairs <- 0                       # Public affairs
political_ideology <- 0                   # Political ideology
social_views <- 0                         # Social views
charity_voluntarism <- 0                  # Charity and voluntarism
demographics <- 0                         # Demographics
public_political <- 0                     # Public affairs + Political ideology
public_political_social <- 0              # + Social views
public_political_social_charity <- 1      # + Charity and voluntarism
public_political_social_charity_demo <- 0 # + Demographics

@@

  # *Q2.2*: How often do you follow international news? 
    "Follow international news: ", 
    c("Sometimes", "Always")

@@

```{r plot-marginals}
# Plot marginals
if (intercept == 1) {
  draws %>%
    mutate(
      levels = factor(i, labels = level_labels)
    ) %>%
    ggplot(aes(x = Gamma, y = levels)) +
    stat_halfeye(.width = .95) +
    geom_vline(xintercept = 0, color = "grey") +
    labs(y = "Attribute Levels")
}
if (intercept != 1) {
  draws %>%
    filter(j != 1) %>%
    mutate(
      levels = factor(i, labels = level_labels),
      covariates = factor(j, labels = covariate_labels)
    ) %>%
    ggplot(aes(x = Gamma, y = covariates)) +
      stat_halfeye(.width = .95) +
      geom_vline(xintercept = 0, color = "white") +
      labs(y = "Covariates") +
      facet_wrap(~ levels, ncol = 5)
}

# Save plot
if (intercept == 1) file_name <- paste("marginal-posteriors_intercept.png")
if (public_affairs == 1) file_name <- paste("marginal-posteriors_public-affairs.png")
if (political_ideology == 1) file_name <- paste("marginal-posteriors_political-ideology.png")
if (social_views == 1) file_name <- paste("marginal-posteriors_social-views.png")
if (charity_voluntarism == 1) file_name <- paste("marginal-posteriors_charity-voluntarism.png")
if (demographics == 1) file_name <- paste("marginal-posteriors_demographics.png")
if (public_political == 1) file_name <- paste("marginal-posteriors_public-political.png")
if (public_political_social == 1) file_name <- paste("marginal-posteriors_public-political-social.png")
if (public_political_social_charity == 1) file_name <- paste("marginal-posteriors_public-political-social-charity.png")
if (public_political_social_charity_demo == 1) file_name <- paste("marginal-posteriors_public-political-social-charity-demos.png")
if (intercept == 1) width_length <- c(10, 10)
if (intercept != 1) width_length <- c(20, 20)
if (public_political_social_charity == 1) width_length <- c(20, 30)
if (public_political_social_charity_demo == 1) width_length <- c(20, 30)
ggsave(
  file_name,
  path = here::here("analysis", "output", "figures"),
  width = width_length[1],
  height = width_length[2],
  units = "in"
)
```
